An Adolescent Mini-Neptune in the Kepler Field

### 2021-06-05 paper/ms.tex
add Q15 2min fitting

>>>>

Our default stellar variability model (RotGPtransit) allows for a
\texttt{RotTerm} GP kernel, with a logjitter term to inflate the
uncertainties to account for excess white noise.
(This results in an inflation of the uncertainties by a factor
of about three).

We considered including an additive \texttt{SHOTerm} kernel to account
for stochastic noise (RotStochGPtransit).  This didn't seem to affect the results much, so
we opted for the simpler model.
